% !TEX root = Simulation.tex

\chapter{DNA Computing - Text Chapter 9}


\section{ Problem 1 }
\textbf{ Name four problems that cannot be solved by a Turing machine. } \\
The Halting Problem, Mortality Problem, Busy Beaver Champion, and Rice's Theorem are four problems that cannot be solved by a Turing Machine. Undecidable problems is the type of problem that a Turing machine cannot solve. These require a yes/no answer, however, there isn't a possible computer program that will always give a right answer. It would sometimes give the wrong answer or run forever without giving an answer. Descriptions of algorithms taken from Wikipedia.
\begin{itemize}
	\item The Halting Problem: Problem of determining, from a description of an arbitrary computer program and an input, whether the program will finish running or continue to run forever.
	\item Mortality Problem: Given a Turing machine, decide whether it halts when run on any configuration(Not necessarily a starting one).
	\item Busy Beaver Champion: A Turing machine that attains the maximum number of steps performed, or maximum number of non blank symbols finally on the tape, among all Turing machines in a certain class. The Turing machines in this class must meet certain design specifications and are required to eventually halt after being started with a blank tape.It is undecidable by a general algorithm whether an arbitrary Turing machine is a busy beaver.
	\item Rice's Theorem:for any non-trivial property of partial functions, there is no general and effective method to decide whether an algorithm computes a partial function with that property.
\end{itemize}

\section{ Problem 2 }
\textbf{ Name four NP-complete and four NP-hard problems. } \\
The Traveling Salesmen Problem (TSP), Himiltonian Path Problem, Satisfiability Problem for Propositional Formulas or Propositions (SAT) Problem, and the Knapsack Problem are four NP-complete problems. The Halting Problem, Cook's Theorem, Maximum Clique Size (from3SAT), and Vertex Cover (from Independent Set) are NP-Hard Problems.

\section{ Problem 5 }
\textbf{ The two most basic DNA sequencing techniques are known as a) Maxam-Gilbert and b) Sanger, after their proponents. Explain how each of these techniques work and contrast them. }\\
\newline
\textbf{Maxam-Gilbert}
The Maxam-Gilbert DNA sequencing technique was developed during 1976-1977. The first step is to radioactively label one end of the DNA fragment. Next, a chemical treatment is used to break a small sample of one or two of the four bases. The modification chemicals are controlled such that the concentration of them will introduce an average of one modification per DNA molecule. The modified DNA may then be cleaved by hot piperidine at the modified base. This labels the DNA fragments.\\
Next, the fragments of the reactions are separated based on size in a gel substance. Then the gel is exposed to an X-ray film to visualize the fragments. Dark bands on the film show the location of identical labeled molecules. \\
\newline
\textbf{Sanger}
The Sanger DNA sequencing technique was developed in 1977. It separates the two DNA strands and the strand to be sequenced is copied. However, the copied strand has chemically altered bases so that when a specified base is reached, it stops copying. The process is done for all four bases and then put back together like a puzzle to see the original piece of DNA.\\
\newline
Both techniques both use chemical reactions, however the Sanger technique requires the DNA to be cloned whereas the Maxam-Gilbert technique can use the raw DNA without prior modification to begin the sequencing. 